Supercritical fluid extraction of essential oil from chamomile flowers: modelling, and parameter estimation

### 2024-02-22 SFE_article_Parameter_Estimation - Chamomile/Sections/Results_Chamomile.tex
22.02

	The parameter estimation problem was solved multiple times for different initial guesses. Each time series was fitted to the model separately. First, the model with linear extraction kinetics was the only one fitted to the dataset. The Figure shows the parameter estimation result for dataset 1, corresponding to the following operating conditions: $40^\circ C$, 100 bar and 6.67$\times 10^{-5}$ kg/s.

@@

	In the case of the model with linear kinetic, two parameters are unknown, namely the partition coefficient $k_m$ and the internal diffusion coefficient $D_i$. Figure \ref{fig: Fit_1_linear} shows the cost function's parameter space and corresponding values. As the cost function is to be minimized, the lowest value of $-\ln(L)$ indicate the best fit. A black vertical stripe at $D_i \approx 0.2$ can be observed. That stripe indicates the existence of the optimal value of the $D_i$. In the direction of $k_m$, the cost function is almost flat, which suggests that any value of $k_m$ above 0.1 fits the data equally well. If $k_m$ can be an arbitrary point, then it can grow to infinity, which suggests that the solvent is far from the saturation, and the model can be simplified. The model reduction can be introduced by considering the limit of $k_m$ in the extraction kinetic term:

	{\footnotesize
		\begin{equation*}
			\begin{split}
				&\lim_{k_m \rightarrow \infty} \left({\color{black}{\color{black} c_s} }(t,z)  - \cfrac{{\color{black}\rho_s}}{{\color{black}k_m}({\color{black}T}(t,z)){\color{black}\rho}({\color{black}T}(t,z),{\color{black}P}(t))}  {\color{black}c_f}(t,z) \right)  = \\
				&= \left({\color{black}{\color{black} c_s} }(t,z)  - \cfrac{{\color{black}\rho_s}}{\infty{\color{black}\rho}({\color{black}T}(t,z),{\color{black}P}(t))}  {\color{black}c_f}(t,z) \right) = \left({\color{black}{\color{black} c_s} }(t,z) - 0 \right)
			\end{split}
	\end{equation*} }

	The extraction model can be modified to account for the reduced kinetic term and the axial diffusion. In such a configuration, two parameters are unknown: internal diffusion coefficient $D_i$ and axial diffusion coefficient $D_e^M$. Figure \ref{fig: Fit_1_Di_Dx} shows the parameter space and corresponding values of the cost function.

@@

	Similarly to the previous case, the optimal value of $D_i$ exists, but a unique value for the $D_e^M$ cannot be determined. A little influence of the axial diffusion coefficient can be observed in Figure \ref{fig: Fit_1_Di_Dx} in a width range of values. By selecting $D_e^M$, which has a low value, the axial diffusion term can be reduced and removed from the model without losing generality. Similar was drawn by \citet{Rahimi2011}, who worked with the same dataset and obtained Peclet numbers from 290 to 400. Such high values of the Peclet number suggest that the advection term dominates the mass transfer, and the axial diffusion is negligible.

	In both cases discussed above, none of the fitting results were satisfactory. Following the idea behind the Broken-and-Intact and Shrinking Core models (presented in Chapter \ref{CH: Gamma_Function}), the gamma function is introduced to account for the decaying extraction kinetic. The proposed correction factor is combined with the reduced linear model, which leads to a new two-parameter ($D_i^R$ and $\Upsilon$) model defined by Equation \ref{Model_kinetic}. Figure \ref{fig: Fit_1_Di_Dx} shows the parameter space with and the corresponding values of the cost function.

	\begin{figure}[!h]
		\centering
		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Parameter_space_Di_Gamma_dataset_1_org.png}
		\caption{Parameter space for the modified extraction model and experiment 1}
		\label{fig: Fit_1_Di_Gamma}
	\end{figure}

	The parameter space of the modified model is characterized by the unique minimum value, which corresponds to the solution of the parameter estimation problem for experiment 1. The red circle shows the minimum value of the cost function found by the optimizer. The remaining experiments are fitted to the modified extraction model, and results are presented in Figure \ref{fig: Fit_Di_Gamma}. The obtained results show good agreement with experimental data.

	\begin{figure}[!h]
		\centering
		\begin{subfigure}[b]{\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_1_4.png}
			\caption{Results of parameter estimation for experiments at $6.67\times 10^{-5}$ [kg/s] and temperature of 40 $[^\circ C]$}
			\label{fig: Fit_1_4_Di_Gamma}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_5_8.png}
			\caption{Results of parameter estimation for experiments at $6.67\times 10^{-5}$ [kg/s] and temperature of 30 $[^\circ C]$}
			\label{fig: Fit_5_8_Di_Gamma}
		\end{subfigure}
		\hfil
		\begin{subfigure}[b]{\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_9_12.png}
			\caption{Results of parameter estimation for experiments at $3.33\times 10^{-5}$ [kg/s]}
			\label{fig: Fit_9_12_Di_Gamma}
		\end{subfigure}
		\caption{Parameter estimation results}
		\label{fig: Fit_Di_Gamma}
	\end{figure}

	The estimated parameters describe the decaying rate of internal diffusion coefficient $D_i$ according to Equation \ref{EQ: C_sat_function}. The internal diffusion coefficient is assumed to decrease as it is more difficult for a solute particle to diffuse from a particle core than the particle of a solute located next to the surface. The obtained decaying patterns are present in Figure \ref{fig: Gamma_function}. It can be noticed from the plot that a higher internal diffusion coefficient characterises the high-pressure fluid. This is in agreement with the work of \citet{Giddings1968}, \citet{Gurdial1989} and \citet{Machida2011} who analysed the solvation power of a solvent and correlated it with physical properties of $CO_2$. The Hildebrand solubility parameter was used to measure the cohesive energy density of a substance. \citet{Giddings1968} proposed a correlation for a solubility parameter $\delta_H[\text{MPa}^{1/2}] = 1.25 P_c^{1/2}\rho_r$, where $P_c$ and $\rho_r$ are critical pressure and reduced density respectively. \citet{Marcus2006} derived a similar correlation from the Van der Waals equation of state: $\delta_H[\text{MPa}^{1/2}] = 2.79 P_c^{1/4}T_r^{1/4}\rho_r$. Figure \ref{fig: Gamma_function} shows that fluid characterised by a higher solubility factor has larger values of internal diffusion coefficient. The relation between $\delta_H$ and $D_i$ should only be treated as an indicator because the system is non-ideal, and external factors such as fluid velocity are not considered.

@@

	The parameter estimation results are combined to analyse the relationship between the obtained parameters and the operating conditions. This work does not apply the traditional approach for finding correlations by combining Reynolds, Schmidt and Sherwood numbers because the axial diffusion was considered negligible. Instead, the Reynolds number $\left(Re = \frac{(2r) \cdot \rho_f \cdot u}{\mu}\right)$ is used solely as an independent variable as shown in Figure \ref{fig: Correlations}. Using the Reynolds number has the advantage of considering the influence of all the control variables (temperature, pressure and flow rate), which means it can be uniquely defined by selecting operating conditions.	
	Two data clusters can be distinguished in Figures \ref{fig: Correlations_Di_Re} and \ref{fig: Correlations_Gamma_Re}, where each cluster corresponds to a different mass flow rate. Even though a linear trend characterises both correlations, correlations related to $D_i^R$ decrease with Re while the correlations related to $\Upsilon$ increase with Re. Higher fluid density and corresponding mass transfer resistance can explain the decrease of the $D_i^R$ along each line. On the other hand, the increase in $\Upsilon$ correlations can be justified by higher solubility. The Hildebrand solubility factor is mainly a function of fluid density, which is also present in the the Reynolds number hence $\Upsilon$ can be correlated with Re.

>>>>

	To solve the parameter estimation problem, the single shooting method was used to transform the boundary-value problem into the initial value problem and to formulate the non-linear programming problem. This non-linear optimization task was tackled using the CasADi framework (\citet{Andersson2018}). Each time series was fitted separately to the model with the linear extraction kinetics (Equation \ref{Model_kinetic_no_sat}). The initial value problem was solved multiple times with varying initial guesses to identify the global minimum. Within the model context characterized by linear kinetics, two parameters remain to be determined: the partition coefficient $k_m$ and the internal diffusion coefficient $D_i$.

@@

	Figure \ref{fig: Fit_1_linear} shows the parameter space and corresponding values of the cost function for experiment 1 ($40^\circ C$, 100 bar and 6.67$\times 10^{-5}$ kg/s). As the cost function is to be minimized, the lowest value of $-\ln(L)$ indicate the best fit. A black vertical stripe at $D_i \approx 0.2$ can be observed. That stripe indicates the existence of the optimal value of the $D_i$. In the direction of $k_m$, the cost function is almost flat, which suggests that any value of $k_m$ above 0.1 fits the data equally well. If $k_m$ can be an arbitrary point, then it can grow to infinity, which suggests that the solvent is far from the saturation, and the model can be simplified. The model reduction can be introduced by considering the limit of $k_m$ in the extraction kinetic term:

	{\footnotesize
		\begin{equation*}
			\begin{split}
				&\lim_{k_m \rightarrow \infty} \left({\color{black}{\color{black} c_s} }(t,z)  - \cfrac{{\color{black}\rho_s}}{{\color{black}k_m}({\color{black}T}(t,z)){\color{black}\rho}({\color{black}T}(t,z),{\color{black}P}(t))}  {\color{black}c_f}(t,z) \right)  = \\
				&= \left({\color{black}{\color{black} c_s} }(t,z)  - \cfrac{\rho_s}{\infty \cdot \rho(T(t,z),P(t))}  {c_f}(t,z) \right) = \left(c_s(t,z) - 0 \right)
			\end{split}
	\end{equation*} }

	The extraction model can be adapted to incorporate adjustments for the reduced kinetic term and axial diffusion. In this revised setup, two parameters remain undetermined: the internal diffusion coefficient $D_i$ and the axial diffusion coefficient $D_e^M$. Figure \ref{fig: Fit_1_Di_Dx} illustrates the parameter space and associated cost function values.

@@

	Similarly to the previous case, the optimal value of $D_i$ exists, but a unique value for the $D_e^M$ cannot be determined. Figure \ref{fig: Fit_1_Di_Dx} illustrates the minimal impact of the axial diffusion coefficient, where a broad range of $D_e^M$ yields identical cost function values. By selecting a low value $D_e^M$, the axial diffusion terms can be reduced or eliminated from the model without compromising its generality. This observation aligns with the findings of \citet{Rahimi2011}, who analysed the same dataset and reported Peclet numbers ranging between 290 and 400. Such high values of the Peclet number suggest that the advection term dominates the mass transfer, and the axial diffusion is negligible.

	In both scenarios previously discussed, the fitting outcomes were not deemed satisfactory. Building upon the concepts underlying the Broken-and-Intact and Shrinking Core models (detailed in Chapter \ref{CH: Gamma_Function}), a gamma function is introduced to capture the diminishing extraction kinetics. The correction factor is combined with the simplified linear model, resulting in a two-parameter model ($D_i^R$ and $\Upsilon$) as given by Equation \ref{Model_kinetic}. Figure \ref{fig: Fit_1_Di_Gamma} shows the parameter space and the corresponding cost function values.

	\begin{figure}[!h]
		\centering
		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=0.98\columnwidth]{/Results_estimation/Parameter_space_Di_Gamma_dataset_1_org.png}
		\caption{Parameter space for the modified extraction model and experiment 1}
		\label{fig: Fit_1_Di_Gamma}
	\end{figure}

	The parameter space for the revised model exhibits a distinct minimum value corresponding to the solution of the parameter estimation problem for experiment 1. The red circle highlights the minimum value of the cost function found by the optimizer. The remaining experiments are fitted to the modified extraction model, and results are presented in Figure \ref{fig: Fit_Di_Gamma}. The obtained results show good agreement with experimental data.

	\begin{figure}[!h]
		\centering
		\begin{subfigure}[b]{\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_1_4.png}
			\caption{Results of parameter estimation for experiments at $6.67\times 10^{-5}$ [kg/s] and temperature of 40 $[^\circ C]$}
			\label{fig: Fit_1_4_Di_Gamma}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_5_8.png}
			\caption{Results of parameter estimation for experiments at $6.67\times 10^{-5}$ [kg/s] and temperature of 30 $[^\circ C]$}
			\label{fig: Fit_5_8_Di_Gamma}
		\end{subfigure}
			\end{figure}%
		\begin{figure}[h!]\ContinuedFloat
		\begin{subfigure}[b]{\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_9_12.png}
			\caption{Results of parameter estimation for experiments at $3.33\times 10^{-5}$ [kg/s]}
			\label{fig: Fit_9_12_Di_Gamma}
		\end{subfigure}
		\caption{Parameter estimation results}
		\label{fig: Fit_Di_Gamma}
	\end{figure}

	The estimated parameters describe the diminishing trend of the internal diffusion coefficient $D_i$, as delineated by Equation \ref{EQ: C_sat_function}. It is hypothesized that the internal diffusion coefficient decreases because solute particles face greater difficulty diffusing from the core of a particle than from positions closer to the surface. Decay patterns under various operational conditions, depicted in Figure \ref{fig: Gamma_function}, show that the internal diffusion coefficient is notably higher in fluids under high pressure. This observation aligns with the findings of \citet{Giddings1968}, \citet{Gurdial1989}, and \citet{Machida2011}, who explored the solvation capability of solvents and its correlation with the physical properties of $CO_2$ by calculating the Hildebrand solubility parameter $\delta_H$. \citet{Giddings1968} introduced a correlation for the solubility parameter $\delta_H[\text{MPa}^{1/2}] = 1.25 P_c^{1/2}\rho_r$, with $P_c$ and $\rho_r$ representing the critical pressure and reduced density, respectively. Similarly, \citet{Marcus2006} formulated a correlation based on the Van der Waals equation of state: $\delta_H[\text{MPa}^{1/2}] = 2.79 P_c^{1/4}T_r^{1/4}\rho_r$. As Figure \ref{fig: Gamma_function} shows, fluids with higher solubility factors exhibit greater internal diffusion coefficients. However, the relationship between $\delta_H$ and $D_i$ should be considered indicative rather than definitive due to the non-ideal nature of the system and the omission of external factors such as fluid velocity.

@@

	The parameter estimation results are combined to analyse the relationship between the obtained parameters and the operating conditions. Unlike traditional methods that employ a combination of Reynolds, Schmidt, and Sherwood numbers to find correlations—omitted here due to the insignificance of axial diffusion—the approach in this study leverages the Reynolds number $\left(Re = \frac{(2r) \cdot \rho_f \cdot u}{\mu}\right)$ as the sole independent variable. Using the Reynolds number has the advantage of considering the influence of all the control variables (temperature, pressure and flow rate), which means it can be uniquely defined by selecting operating conditions.

	In Figures \ref{fig: Correlations_Di_Re} and \ref{fig: Correlations_Gamma_Re}, two distinct data clusters emerge, each corresponding to a different mass flow rate. Despite the linear trends observed in both sets of correlations, the correlations for $D_i^R$ exhibit a decline with increasing Re, whereas those for $\Upsilon$ show an upward trend with Re. The decrease in $D_i^R$ across each data line can be attributed to higher fluid density and increased mass transfer resistance. Conversely, the rise in $\Upsilon$ correlations may be explained by enhanced solubility. The Hildebrand solubility factor and the Reynolds number are proportional to the fluid density; hence, $\Upsilon$ can be correlated with Re.

### 2024-02-22 SFE_article_Parameter_Estimation - Chamomile/Sections/introduction_imp.tex
22.02

	The present study focuses on extracting essential oil from the caraway (Carum carvi L.) seeds with supercritical fluid extraction and modelling that process. Caraway is a biennial plant belonging to the Apiaceae family. It is widespread in Asia, Europe, and North Africa. The essential oil obtained from caraway finds its potential application as a fragrance ingredient in perfumes, liquors, and toothpaste. As presented by \citet{Hromis2015}, the dried caraway contains nearly~2.8–5\% essential oil, from which the main compounds are carvone, pinene, camphene, limonene, and carveol.

	The economic feasibility of the process is crucial when selecting the appropriate technology. Conventional processes, such as distillation and organic solvent extraction, are frequently used for essential oil extraction. The distillation process is carried out at a high temperature, which causes thermal degradation of thermolabile compounds—considering that alternative techniques like supercritical fluid extraction gained popularity for extraction. Supercritical carbon dioxide, in particular, is attractive due to its unique properties such as inflammable, non-toxic, low critical temperature and non-corrosive. Furthermore, its critical point is relatively low compared to other fluids, making it a suitable alternative to traditional extraction techniques. The supercritical fluids exhibit both gas- and liquid-like properties so that operating conditions can adjust pressure-depended dissolving power.

	Various mathematical models have been proposed to describe the extraction of valuable compounds from a fixed biomass bed. However, selecting an appropriate extraction model requires understanding the physical phenomena occurring in the operational unit. Each model has its own set of assumptions and describes different mass transfer mechanisms and equilibrium relationships.

	One model proposed by \citet{Reverchon1993} is the hot ball model, which is based on an analogy to heat transfer and describes an extraction process from solid particles containing small quantities of solute where solubility is not a limiting factor. Another model, the Broken-and-Intact Cell model, was presented by \citet{Sovova1994}. This model describes a system where the outer surfaces of particles have been mechanically interrupted, allowing easy access of solvent to the solute from the broken cells. In contrast, the solute from the intact cells is less accessible due to high mass transfer resistance.

	\citet{Reverchon1996} developed a model for fluid-solid extraction, where the oil is treated as a single component, and the extraction process is controlled by internal mass transfer resistance, neglecting external mass transfer. However, this model does not consider the influence of axial dispersion or changes in fluid density and flow rate along the bed.

	In this work, the fundamental governing equations are derived and combined with the kinetic model suggested by \citet{Reverchon1996} to obtain a general model for the oil extraction process from the caraway seed. This model simplifies some of the physical behaviour to obtain a control-oriented model. It is assumed that the extraction process operates semi-continuously in a cylindrical vessel. The solvent is first brought to supercritical conditions, pumped through a fixed bed of finely chopped biomass, and the solute is extracted from the biomass. The solvent and solute are then separated in a flush drum, and the extract is collected. The feed flow rate ($F_{in}$) and inlet temperature ($T_{in}$) of the extractor can be measured and manipulated, while the vessel pressure ($P$) can also be measured and manipulated. However, the outlet temperature ($T_{out}$) can only be measured. Figure \ref{fig: SFE_drawing} shows a simplified flow diagram.

@@

	This study aims to develop a process model for extracting natural substances from solid materials and liquids using supercritical fluids, specifically supercritical $CO_2$. To achieve this, the model parameters are estimated based on thermodynamic relations and a set of experiments conducted at various conditions. The maximum likelihood estimator is used to solve the parameter estimation problem, and the obtained parameters are subjected to regression to derive correlations. These correlations enable the process model to be generalized across a range of temperatures (40 to $50~^\circ C$) and pressures (200 to 300 bar).

	The study is structured as follows: Chapter \ref{CH: Thermodynamic} provides a general discussion on supercritical fluids to familiarize the reader with their properties. Chapter \ref{CH:Governing_equations_chapter} introduces the general balance equations. The balance equations are combined with the extraction kinetic equation to develop the process model in Chapter \ref{CH: Extraction_model}. The maximum likelihood technique is presented in Chapter \ref{CH: Parameter_estimation} and is then combined with the process model. Chapter \ref{CH: Experiments} describes the experimental work and the data collected from experiments are used to estimate missing parameters related to the extraction kinetic. Finally, the parameter estimations and simulation results are discussed in Chapters \ref{CH: Results} and \ref{CH: Conclusion}

>>>>

	This study investigates the extraction of essential oil from chamomile flowers (Matricaria chamomilla L.) via supercritical fluid extraction techniques and modelling of this process. Chamomile is a medicinal herb widely cultivated in southern and eastern Europe—such as Germany, Hungary, France, and Russia. It can be found outside of Europe in Brazil as discussed by \citet{Singh2011}. This plant is distinguished by its hollow, bright gold cones, housing disc or tubular florets and surrounded by about fifteen white ray or ligulate florets. Chamomile has been used for its medicinal benefits, serving as an anti-inflammatory, antioxidant, mild astringent, and healing remedy. Chamomile's aqueous extract is widely used as a gentle sedative to calm nerves and mitigate anxiety, hysteria, nightmares, insomnia, and other sleep-related conditions, according to \citet{Srivastava2009}. \citet{Orav2010} reported that oil yields from dried chamomile samples ranged from 0.7 to 6.7 mL kg$^{-1}$. Notably, the highest yields of essential oil, between 6.1 and 6.7 mL kg$^{-1}$, were derived from chamomile sourced from Latvia and Ukraine, while chamomile from Armenia exhibited a lower oil content of 0.7 mL kg$^{-1}$.

	%The present study focuses on extracting essential oil from the chamomile flowers with supercritical fluid extraction and modelling that process. Caraway is a biennial plant belonging to the Apiaceae family. It is widespread in Asia, Europe, and North Afri``ca. The essential oil obtained from caraway finds its potential application as a fragrance ingredient in perfumes, liquors, and toothpaste. As presented by \citet{Hromis2015}, the dried caraway contains nearly~2.8–5\% essential oil, from which the main compounds are carvone, pinene, camphene, limonene, and carveol.

	%The economic feasibility of the process is crucial when selecting the appropriate technology. Conventional processes, such as distillation and organic solvent extraction, are frequently used for essential oil extraction. The distillation process is carried out at a high temperature, which causes thermal degradation of thermolabile compounds—considering that alternative techniques like supercritical fluid extraction gained popularity for extraction. Supercritical carbon dioxide, in particular, is attractive due to its unique properties such as being inflammable, non-toxic, low critical temperature, and non-corrosive. Furthermore, its critical point is relatively low compared to other fluids, making it a suitable alternative to traditional extraction techniques. The supercritical fluids exhibit both gas- and liquid-like properties so that operating conditions can adjust the dissolving power.

	%Various mathematical models have been proposed to describe the extraction of valuable compounds from a fixed biomass bed. However, selecting an appropriate extraction model requires understanding the physical phenomena occurring in the operational unit. Each model has its own set of assumptions and describes different mass transfer mechanisms and equilibrium relationships.

	%One model proposed by \citet{Reverchon1993} is the hot ball model, which is based on an analogy to heat transfer and describes an extraction process from solid particles containing small quantities of solute where solubility is not a limiting factor.

	%Another model, the Broken-and-Intact Cell model, was presented by \citet{Sovova1994}. This model describes a system where the outer surfaces of particles have been mechanically interrupted, allowing easy access of solvent to the solute from the broken cells. In contrast, the solute from the intact cells is less accessible due to high mass transfer resistance.

	%\citet{Reverchon1996} developed a model for fluid-solid extraction, where the oil is treated as a single component, and the extraction process is controlled by internal mass transfer resistance, neglecting external mass transfer. However, this model does not consider the influence of axial dispersion or changes in fluid density and flow rate along the bed.

	%In this work, the fundamental governing equations are derived and combined with the kinetic model suggested by \citet{Reverchon1996} to obtain a general model for the oil extraction process from the chamomile flower. This model simplifies some of the physical behaviour to obtain a control-oriented model. It is assumed that the extraction process operates semi-continuously in a cylindrical vessel. The solvent is first brought to supercritical conditions, pumped through a fixed bed of finely chopped biomass, and the solute is extracted from the biomass. The solvent and solute are then separated in a flush drum, and the extract is collected. The feed flow rate ($F_{in}$) and inlet temperature ($T_{in}$) of the extractor can be measured and manipulated, while the vessel pressure ($P$) can also be measured and manipulated. However, the outlet temperature ($T_{out}$) can only be measured. Figure \ref{fig: SFE_drawing} shows a simplified flow diagram.

	Evaluating the economic viability of the process is essential when choosing the suitable technology for essential oil extraction. Traditional methods, such as distillation and organic solvent extraction, are commonly employed but come with drawbacks. Distillation, for example, involves high temperatures that can lead to the thermal degradation of heat-sensitive compounds. This limitation has led to the increased popularity of alternative techniques like supercritical fluid extraction. Supercritical carbon dioxide is particularly appealing due to its distinctive properties: it's inflammable, non-toxic, has a low critical temperature, and is non-corrosive. Moreover, its relatively low critical point, compared to other fluids, positions it as an advantageous alternative to conventional extraction methods. Supercritical fluids are capable of exhibiting both gas- and liquid-like properties, allowing for adjustable dissolving power through changes in operating conditions.

	The literature offers a variety of mathematical models aimed at detailing the extraction of valuable compounds from a fixed biomass bed. Selecting a fitting model necessitates a deep understanding of the physical processes at play within the operational unit, as each model is built on specific assumptions and outlines distinct mass transfer mechanisms and equilibrium dynamics.

	One model proposed by \citet{Reverchon1993} is the hot ball model, which is based on an analogy to heat transfer and describes an extraction process from solid particles containing small quantities of solute where solubility is not a limiting factor.

	The Broken-and-Intact Cell model, proposed by \citet{Sovova1994}, assumes that external surfaces of particles are mechanically disrupted, allowing the solvent's access to the solute in broken cells, while the solute in intact cells remains less accessible due to higher mass transfer resistance.

	\citet{Reverchon1996} formulated a fluid-solid extraction model where the solute is treated as a single component, governed by internal mass transfer resistance and omitting the effects of external mass transfer, axial dispersion, and variations in fluid density and flow rate throughout the bed.

	This work builds upon the linear kinetic model suggested by \citet{Reverchon1996}, deriving fundamental governing equations to develop a comprehensive model for the chamomile oil extraction process. This model aims for control-oriented simplicity, assuming a semi-continuous operation within a cylindrical vessel. The process involves supercritical solvent being pumped through a fixed bed of finely chopped biomass to extract the solute, followed by separation of the solvent and solute in a flush drum to collect the extract. Parameters such as the feed flow rate ($F_{in}$) and inlet temperature ($T_{in}$) are adjustable and measurable, as is the vessel pressure ($P$), whereas the outlet temperature ($T_{out}$) can only be monitored. A simplified flow diagram is presented in Figure \ref{fig: SFE_drawing}, illustrating the process setup.

@@

	%This study aims to develop a process model for extracting natural substances from solid materials and liquids using supercritical fluids, specifically supercritical $CO_2$. To achieve this, the solvent properties are estimated based on thermodynamic relations, and the extraction kinetic parameters are estimated based on a set of experiments conducted under various conditions. The maximum likelihood estimator is used to solve the parameter estimation problem, and the obtained parameters are subjected to regression to derive correlations. These correlations enable the process model to be generalized across a range of temperatures (40 to $50~^\circ C$) and pressures (200 to 300 bar).

	%The study is structured as follows: Chapter \ref{CH: Thermodynamic} provides a general discussion on supercritical fluids to familiarize the reader with their properties. Chapter \ref{CH:Governing_equations_chapter} introduces the general balance equations. The balance equations are combined with the extraction kinetic equation to develop the process model in Chapter \ref{CH: Extraction_model}. The maximum likelihood technique is presented in Chapter \ref{CH: Parameter_estimation} and is then combined with the process model. Chapter \ref{CH: Experiments} describes the experimental work and the data collected from experiments, which are used to estimate missing parameters related to the extraction kinetics. Finally, the parameter estimations and simulation results are discussed in Chapters \ref{CH: Results} and \ref{CH: Conclusion}.

	This study focuses on creating a process model for the extraction of natural substances from solid materials using supercritical fluids, with a particular emphasis on supercritical $CO_2$. The approach involves estimating the solvent properties through thermodynamic relationships and determining the extraction kinetic parameters via a series of experiments conducted under a variety of conditions. The maximum likelihood estimator method is employed to address the parameter estimation challenge, with the derived parameters subsequently used to establish correlations. These correlations are instrumental in extending the applicability of the process model across different temperatures (30 to 40$^\circ C$) and pressures (100 to 200 bar).

	The organization of the study is as follows: Chapter \ref{CH: Thermodynamic} offers an overview of supercritical fluids, aiming to acquaint the reader with their unique properties. Chapter \ref{CH:Governing_equations_chapter} outlines the fundamental balance equations. These equations are then integrated with the extraction kinetic equation in Chapter \ref{CH: Extraction_model} to formulate the process model. Chapter \ref{CH: Parameter_estimation} introduces the maximum likelihood estimation technique, which is subsequently applied within the context of the process model. Chapter \ref{CH: Experiments} details the experimental procedures and the data acquisition necessary for estimating the kinetic parameters related to the extraction process. The study culminates in Chapters \ref{CH: Results} and \ref{CH: Conclusion}, where the parameter estimations and simulation outcomes are thoroughly analysed and discussed.
